A \emph{Grimm} idea

### 2016-05-01 paper/main.tex
added tikz pictures

\usepackage{epigraph}
\usepackage[autostyle,german=guillemets]{csquotes}
\usepackage[ngerman, english]{babel}
\usepackage[style=numeric,backend=biber]{biblatex}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{todonotes}
\usepackage{mdframed}

\newtheorem{thm}{Theorem}
\newtheorem{lem}{Lemma}

@@

@@

We can now find the $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble machine we
are looking for.
\begin{thm}
  \label{thm:pebblewalk}
  There is a $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble machine which
  explores every given graph $G$ with bounded degree $\Delta$ either completly
  or at least loops on $n$ distinct vertices.
\end{thm}
\begin{proof}
  The main idea is to use the adapted algorithm $A$ to find for an
  universal exploration sequence for a 3-regular graph from above. Therefore
  we take $G$ and transform it to a 3-regular graph on which $A$ finds the
  corresponding universal exploration sequence. The transformation replaces
  any node $v$ with degree $d$ by $3d$ nodes which then form a circle where
  every nodes has degree $3$. The edges of $v$ are moved to nodes in the
  circle. Specifically the edge with port $i$ is replaced by 3 edges which are
  attached to $(v,i), (v,i+d), (v,i+2d)$. (Note that the other
  vertex attached to the edge is replaced by the same construction and therfore
  offers enough ports for the newly introduced edges.) The following picture
  illustrates this construction:\todo{add picture}

  This simulation yields at most $3\Delta n^{2}$ many nodes and can be emulated
  with $\mathcal{O}(1)$ many memory space since it is only needed to store
  the second component of the inserted nodes which is bounded by $3\Delta$.
  Furthermore $A$ can be run on this constructed Graph and only needs
  $\mathcal{0}(\log n)$ space since $\mathcal{O}(\log(3\Delta n^{2})) =
  \mathcal{O}(\log(3) + \log(\Delta) + 2\log(n)) = \mathcal{O}(\log n)$.
  Which yields the desired $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble
  machine.
\end{proof}

In order to obtain the desired boundary of $\log\log n$ space and $\log\log n$
pebbles we show that a pebble machine can be simulated by storing its tape
content by pebbles that are placed on a closed walk.
\begin{thm}
  \label{thm:simulation}
  For every graph $G$ a $(s,p,2m)$ pebble machine $M$ can be simulated by
  a $(cs,p + c,m)$ pebble machine that simulates the walk of $M$ or explores
  $G$.
\end{thm}
\begin{proof}
  In this proof we will focus on the simulation and we leave out a thorough
  analysis of the space requirements of the simulation since it is rather
  technical but does not add a lot to the idea. Nevertheless we encourage
  interested readers to see \cite{pebbles} for the details.

  The main idea of this simulation is to store the tape of $M$ by pebbles
  placed on a closed walk in the graph. We show that every node on this closed
  walk can be given an index and a pebble placed on a node represents the
  binary representation of the index as the content of $M$'s tape. Therefore we
  first off introduce a variable $m_{1}$ which is dependent on the simulated
  pebble machine $M$ (further requirements on $m_{1}$ and how to obtain it
  can be seen in \cite{pebbles}). We will now take the tape of $M$ and separate
  it into $2m/m_{1}$ blocks of the size $m_{1}$. And each of these blocks is
  encoded by the placement of a pebble on a closed walk $\omega$. So we use
  pebble $p_{0}$ to encode the first $m_{1}$ bits, the pebble $p_{1}$ used to
  encode the next $m_{1}$ bits and so forth. Thus, the pebble $p_{i}$ encodes
  the bits $im_{1},\dots,(i+1)m_{1}-1$. It is therefore necessary that every
  pebble can encode $2^{m_1}$ different states. Therefore we use a closed walk
  $\omega$ which visits at least $2^{m_1}$ distinct vertices yielding $2^{m_1}$
  many \enquote{states} for each pebble (by its placement on this closed walk).
  Therefore we can use the binary representation of the indices of the nodes
  on which the pebbles are placed as the content of the encoded memory block.
  The following picture gives an illustration of this.\todo{add picture}

@@

\section{Barriers}
In the following we will discuss the limits of the exploration approach with
pebbles. Specifically, we will argue that we can construct 3-regular graphs
that any agent with $p$ pebbles cannot traverse. Such graphs are called
$p$-barriers.
Note that connecting a 3-regular graph might violate its 3-regularity.
Therefore we rely on having a distinguishable edge $e$ in the 3-regular graph
which we can delete to connect the vertices $e$ connected to the
\enquote{outside}. This preserves the 3-regularity.
With a given $p$-barrier $H$ we can construct a trap for an agent with $p$
pebbles as follows:
\todo{add picture}

>>>>

\usepackage{epigraph}
\usepackage[autostyle,german=guillemets]{csquotes}
\usepackage[ngerman, english]{babel}
\usepackage[style=numeric,backend=biber]{biblatex}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{todonotes}
\usepackage{mdframed}
\usepackage{wrapfig}

\newtheorem{thm}{Theorem}
\newtheorem{lem}{Lemma}
\newtheorem{ex}{Exercise}

@@

\input{tikz/settings}

@@

We can now find the $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble machine we
are looking for.
\begin{thm}
  \label{thm:pebblewalk}
  There is a $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble machine which
  explores every given graph $G$ with bounded degree $\Delta$ either completly
  or at least loops on $n$ distinct vertices.
\end{thm}
\begin{wrapfigure}{r}{0.6\textwidth}
  \caption{Illustration how to transform any graph to a 3-regular graph.}
  \label{fig:3reg}
  \resizebox{0.6\textwidth}{!}{\input{tikz/regsim}}
\end{wrapfigure}
\begin{proof}
  The main idea is to use the adapted algorithm $A$ to find for an
  universal exploration sequence for a 3-regular graph from above. Therefore
  we take $G$ and transform it to a 3-regular graph on which $A$ finds the
  corresponding universal exploration sequence. The transformation replaces
  any node $v$ with degree $d$ by $3d$ nodes which then form a circle where
  every nodes has degree $3$. The edges of $v$ are moved to nodes in the
  circle. Specifically the edge with port $i$ is replaced by 3 edges which are
  attached to $(v,i), (v,i+d), (v,i+2d)$. (Note that the other
  vertex attached to the edge is replaced by the same construction and therfore
  offers enough ports for the newly introduced edges.) Figure \ref{fig:3reg}
  illustrates this construction.  This simulation yields at most
  $3\Delta n^{2}$ many nodes and can be emulated with $\mathcal{O}(1)$ many
  memory space since it is only needed to store the second component of the
  inserted nodes which is bounded by $3\Delta$. Furthermore $A$ can be run on
  this constructed Graph and only needs $\mathcal{0}(\log n)$ space since
  $\mathcal{O}(\log(3\Delta n^{2})) = \mathcal{O}(\log(3) + \log(\Delta) +
  2\log(n)) = \mathcal{O}(\log n)$. Which yields the desired
  $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble machine.
\end{proof}

In order to obtain the desired boundary of $\log\log n$ space and $\log\log n$
pebbles we show that a pebble machine can be simulated by storing its tape
content by pebbles that are placed on a closed walk.
\begin{thm}
  \label{thm:simulation}
  For every graph $G$ a $(s,p,2m)$ pebble machine $M$ can be simulated by
  a $(cs,p + c,m)$ pebble machine that simulates the walk of $M$ or explores
  $G$.
\end{thm}
\begin{figure}
  \caption{Illustration how to simulate the tape of a pebble machine by
  placing pebbles on a closed walk where $m_{1} = 3$. Note that the first
  $2^{m_{1}}=2^{3}=8$ distinct vertices are used for the simulation but the
  walk can be longer (as indicated by the dotted connection from $7$ to $0$).}
  \label{fig:tapesim}
  \begin{center}
    \resizebox{0.6\textwidth}{!}{\input{tikz/tapesim}}
  \end{center}
\end{figure}
\begin{proof}
  In this proof we will focus on the simulation and we leave out a thorough
  analysis of the space requirements of the simulation since it is rather
  technical but does not add a lot to the idea. Nevertheless we encourage
  interested readers to see \cite{pebbles} for the details.

  The main idea of this simulation is to store the tape of $M$ by pebbles
  placed on a closed walk in the graph. We show that every node on this closed
  walk can be given an index and a pebble placed on a node represents the
  binary representation of the index as the content of $M$'s tape. Therefore we
  first off introduce a variable $m_{1}$ which is dependent on the simulated
  pebble machine $M$ (further requirements on $m_{1}$ and how to obtain it
  can be seen in \cite{pebbles}). We will now take the tape of $M$ and separate
  it into $2m/m_{1}$ blocks of the size $m_{1}$. And each of these blocks is
  encoded by the placement of a pebble on a closed walk $\omega$. So we use
  pebble $p_{0}$ to encode the first $m_{1}$ bits, the pebble $p_{1}$ used to
  encode the next $m_{1}$ bits and so forth. Thus, the pebble $p_{i}$ encodes
  the bits $im_{1},\dots,(i+1)m_{1}-1$. It is therefore necessary that every
  pebble can encode $2^{m_1}$ different states. Therefore we use a closed walk
  $\omega$ which visits at least $2^{m_1}$ distinct vertices yielding $2^{m_1}$
  many \enquote{states} for each pebble (by its placement on this closed walk).
  Therefore we can use the binary representation of the indices of the nodes
  on which the pebbles are placed as the content of the encoded memory block.
  Figure \ref{fig:tapesim} illustrates this.

@@

\section{Barriers}
In the following we will discuss the limits of the exploration approach with
pebbles. Specifically, we will argue that we can construct 3-regular graphs
that any agent with $p$ pebbles cannot traverse. Such graphs are called
$p$-barriers.
Note that connecting a 3-regular graph might violate its 3-regularity.
Therefore we rely on having a distinguishable edge $e$ in the 3-regular graph
which we can delete to connect the vertices $e$ connected to the
\enquote{outside}. This preserves the 3-regularity. The interested reader might
then enjoy the following exercise:
\begin{ex}
  Given a $p$-barrier with $m$ vertices for a agent $A$ with $p$ pebbles.
  Construct a trap for $A$ (with $2m+4$ vertices). 
\end{ex}
